### 2022-07-25 paper/akweury/document.tex
update light

The normal inference task estimate the surface normal of a 3D object. There are two main approach to solve the task. Geometry based approach estimate the surface normal of an object based on the geometry principle. Point cloud is a common surface geometry information which samples the surface point position in 3D space. Another approach is photometric stereo based approach, which utilizes a set of images under different illumination conditions. In this chapter, geometry and photometric stereo based approach are introduced separately, then a deep learning based approach using geometry information is proposed. In the end, as the main work of the thesis, another deep learning method is proposed based on both geometry and photometric stereo information.

\section{Geometry based normal estimation}

\subsection{Approach}
The geometry based normal estimation uses point cloud of the object surface as input.
Given a structured point cloud $ V^{W\times H\times 3} $ to estimate the normal map  $ N^{W\times H \times 3} $, where each normal  $ \textbf{n}^{3\times 1} $ at point $ \textbf{v}^{3\times 1} \in N $ is a unit vector with its direction point outward of the surface and perpendicular to the tangent plane of the surface at point $ \textbf{p}^{3\times 1} $.

The idea behind the neighbor based method is to fit a plane $ \Pi $ using the $ k $ neighbors $ \textbf{p}_1, ..., \textbf{p}_k \in \mathbb{R}^3 $ of the point $ \textbf{p} $, calculate the normal  $ \tilde{\textbf{n}} $ of the plane.

It is under the assumption that the point and its neighbors are located in the same plane. This is usually not hold for the most of the surface, but if $ k $ in a suitable scale and point cloud is dense enough, it is enough to get an accurate and sharp result. As shown in Figure \ref{fig:svd-normal}.

Specifically, it is not necessary to find the exact plane equation to solve the normal. Instead, the normal can be derived based on an equation system. 
The normal $ \tilde{\textbf{n}} $ of plane $ \Pi $ is perpendicular to all the vector on the plane $ \Pi $, we can construct $ k $ vectors on plane $ \Pi $ use  $ k $ neighbors $ \textbf{p}_1, ..., \textbf{p}_k \in \mathbb{R}^3 $ of point $ \textbf{p} $. For the simplicity, we can choose $ \textbf{p}_1 $ as the base point, then $ k-1 $ vectors can be construct as follows
\begin{equation}
	\begin{array}{rr}
		\displaystyle \textbf{v}_i = \textbf{p}_1 - \textbf{p}_i & \text{for}\ i= 2,...,k \\
	\end{array}
\end{equation}
and each of them satisfied $ \textbf{v}_i \cdot \tilde{\textbf{n}} = 0$. Then, the equation system can be constructed as 
\begin{equation}{\label{eq:normal-overdetermined-equation}}
	A \cdot \textbf{n} = 0
\end{equation}
where $ A \in \mathbb{R}^{(k-1)\times 3} $ is the vector matrix vertically stacked by $ \textbf{v}_1, ..., \textbf{v}_{k-1} $.
In order to avoid trivial solution, one more constraint should be added
\[ \|  \bn_{3 \times 1} \|_2^2 = 1  \]
which also let the normal to be a unit vector.

To calculate a valid normal, at least 3 points are required to construct, i.e. $ k>=3 $. For the sake of robust, more points can be used to reduce the measuring error. For the case $ k>3 $, since the surface vectors are actually not in the same plane, the equation system is likely over-determined . Then the equation system mentioned above can be converted to follow optimization problem
\begin{equation}
	\begin{array}{rrclcl}
		\displaystyle \min & \multicolumn{3}{l}{\| A  \bn \|^2} \\
		\\
		\textrm{s.t.} & \| \bn \|^2 & = & 1 
	\end{array}
\end{equation}
which can be solved by singular value decomposition(SVD). Let the decomposition of 
\[ A=U\Sigma V^T \]
The solution i.e. normal is the last column of $ V $.

At last, all the normals should point ot view point $ \textbf{s} $, thus the direction of a normal should be inverted if 
\begin{equation}\label{eq:normal-invertion}
	\textbf{n} \cdot (\textbf{p}  - \textbf{s}) > 0
\end{equation}

Repeat the procedure for all the points in the point cloud to get the entire normal map.

\subsection{Evaluation}
The neighbor based method can predict the normal map in a good way when the given point cloud is dense, as shown in Figure \ref{fig:svd-normal}. It can successfully predict the smooth surface of the dragon object, especially the flakes and the tails of the dragon.

However, it failed in the areas such as hindleg, horn and the mouth, which consists mainly by sharp edges. This is because the neighbors points in these area do not hold the assumption of coplanarity well, the normals of these neighbors can be very different. 
\begin{figure}[th]
	\centering
	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_groundtruth.png}
	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_normal_SVD.png}
	\includegraphics[width=.25\textwidth]{./Figures/svd-synthetic/no-noise/fancy_eval_2_error_SVD.png}

	\label{fig:svd-normal}
	\caption{Normal map of a dragon object predicted by neighbor based method. k=2, angle error=5 \textbf{Left}: ground-truth normal map \textbf{Middle}: predicted normal map, \textbf{Right}: Error map}
\end{figure}
The neighbor based method is depended on a well-chosen parameter $ k $. Figure \ref{fig:svd-k-eval} shows the evaluation on different $ k $ values. When $ k=1 $, the average error of the whole image is the lowest one, most of the normals are close to the ground-truth but the outline edges, which are the areas that surface normal changed extremely sever. For the case $ k=2 $, the sharp edges are more smooth and cause more error, like the eyes area of the dragon. Compare to the first case, the outline edge error goes better. Most of the edge errors are reduced when $ k=2 $, since more neighbor points join the evaluation and it reduces the effect of outliers. However, for the area of horn outline, hindleg outline, the error goes worse. In this case, most of the neighbors of these points are outliers and thus failed this approach.  $ k=3 $ and $ k=4 $ further increase the angle errors based on $ k=2 $.
\begin{figure}[th]
	\centering
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k1.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k2.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k3.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/k-compare/k4.png}	
	\label{fig:svd-k-eval}
	\caption{Error map of neighbor based method with different $ k $ values. From left to right, $ k=1,2,3,4 $ separately.}
\end{figure}

The performance of neighbor based method is good enough for a well chosen $ k $. However, for the case of noised point cloud as input, this approach will broken, since the noise will failed the neighbor assumption and also reduce the number of possible neighbors of each point for a fixed $ k $.
\begin{figure}[th]
	\centering
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_point_cloud_noise.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_groundtruth.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_normal_SVD.png}
	\includegraphics[width=.2\textwidth]{./Figures/svd-synthetic/noise/fancy_eval_2_error_SVD.png}	
	\label{fig:svd-noise}
	\caption{Evaluation of neighbor based method on a noised dragon model}
\end{figure}

% ---------------------- gated convolution neural network ------------------------

\section{Photometric Stereo}
Photometric stereo was initially introduced by \cite{photometric-stereo}, which estimates the surface normal of the object by observing the object in the same position but under different illuminated scenes. It based on the fact that the light reflected by a surface is dependent on the surface normal and the light direction.

\subsection{Approaches}
Given an image $ I $, it can be decomposed in to two parts, the reflectance $ R $ and the shading $ S $,
\[ I = R\oplus S\]
where $ \oplus $ denotes the element-wise product. This decomposition of the image is based on the intrinsic image model, which proposed by  \cite{intrinsic-image}. It interprets the observed image into reflectance image and the shading image. As shown in Figure \ref{fig:intrinsic-image}
%% insert a image for decompositions
\begin{figure}[th]
	\centering
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_reflectance.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_shading.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_light.png}}
	{\includegraphics[width=.18\textwidth]{./Figures/intrinsic_image_normal.png}}
	\caption{Intrinsic image analysis of the bus object. From left to right, original image, reflectance image, shading image, light image, normal image}
	\label{fig:intrinsic-image}
\end{figure}

The equation can be further decomposed based on different surface models. If assume the object surfaces are Lambertian surfaces, i.e. the surface which reflect light in all directions, the shading image can be decomposed as the product of the  radiance of  incoming light $ L_0 $, the cosine of the angle of incidence, which is the dot product of the surface normal $ N $ and the light source direction $ L $.
\[ I = \rho  \odot ( L_0 \textbf{L} \cdot  \textbf{N}) \]
note that the surface normal $ N $ and light direction $ L $ are unit vectors thus they have only two degrees of freedom.

\begin{figure}[th]
	\centering
	\begin{tikzpicture} 
		% reference lines
		\coordinate (light) at (-1,3);
		\coordinate (p) at (2,0);
		\coordinate (normal) at (2,3);
		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
	\end{tikzpicture}
	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
	\label{fig:lambertian-surface}
\end{figure}

The equation can be further rearranged as follows
\[ I = \textbf{g} \cdot \textbf{L} =(L_0\rho \odot \textbf{N}) \cdot  ( \textbf{L}) \]
The shape from shading method employed the equation mentioned above to predict the both surface albedo $ \rho $ and the normal $ \textbf{N} $ with knowning light source direction $ \textbf{L} $. More specifically, a set of $ k $ image for the same scene have been captured based on different light projections. Then, for each pixel $ (x,y) $ in the image, an equation system can be set up

\[ 
\begin{pmatrix}
	L_1^T \\
	L_2^T \\
	\cdots \\
	L_k^T
\end{pmatrix} g(x,y) = 
\begin{pmatrix}
	I_1(x,y) \\
	I_2(x,y) \\
	\cdots \\
	I_3(x,y)
\end{pmatrix}
\]
for the simplicity, $ L_i^T $ for $ 1\le i \le k $ denotes the light direction at position $ (x,y) $ in the image $ k $ 
The equation can be solved based on least square methods. 
Since normal $ N(x,y) $ is unit vector, thus we have

\[ \|g(x,y)\|_2 = \|L_0\rho(x,y)N(x,y)\|_2 = L_0\rho(x,y) \]

Then the normal can be obtained as follow

\[  N(x,y) = \frac{g(x,y)}{L_0\rho(x,y)}\]

In another word, the surface normal including the albedo can be obtained directly based on a set of images and light directions.

\section{Gated Convolution neural network for surface normal estimation}
\label{sec:gcnn}

Recently, deep learning based method achieved a great succeed for image processing. ( \cite{yolov3}, \cite{efficientDet}) These network architectures use a batch of RGB / Grayscale images as input and are employed for classification problems. Usually, the images are convoluted with a convolution layer and downsampling with pooling layers. The outputs of the network consist of a single value to represent the index of the corresponding class (\cite{efficientDet}) or with a set of values to represent the position of bounding boxes.(\cite{yolov3}). However, in many other vision tasks, like normal map inference, the output is demanded as the same shape as the input. Instead of predicting one or several classes for the whole input matrix, the class for each pixel requires for prediction. In this case, the traditional network architecture is not suitable anymore.

%% upsampling 
It is worth to noticed that, the output of normal inference CNN model is not one or several labels but an entire image or normal map with same size. 
%% talk about image upsampling, unet
Recently,\cite{unet} proposed an architecture called UNet for biomedical image segmentations. The architecture is shown in Figure \ref{fig:u-net}.The first half network is a usual classification convolutional network, the second half replace the pooling layers and traditional fc layers in the traditional CNNs to upsampling layers, thus in the end of the second half, the output is able to back to the input size. The proposed network can successfully assigned each pixel a class for segmentation tasks. Under this symmetric network, an input image is downsampled 4 times and upsampled 4 times. Output image has exactly the same size as input image. The downsampling and upsampling both have large number of feature channels, which guarantee the network propagates the information to higher resolution layers.

\begin{figure}[th]
	\centering
	\includegraphics[width=.8\textwidth]{./Figures/u-net-illustration-correct-scale2.pdf}
	\label{fig:u-net}
	\caption{The structure of UNet. \cite{unet}}
\end{figure}

The UNet is based on standard convolution layers to construct the network. This is reasonable for image processing task with full-dense input, since no missing pixels exist. 
However, for the input of noised point cloud, the valid and invalid pixels will be treated equally if we still perform standard convolution layers. Since the aim of the network is not learning the pattern of noise, but the noise with eternally changing patterns will confuse the network, and it fails the normal inference, a mask is required to distinguish two kinds of pixels.

% why we need a mask
\cite{pncnn0} use binary mask to indicate valid pixels, and further use normalized convolution to predict the output. The normalized convolution is shown as follows

\begin{equation}
	\begin{array}{rrclcl}
		O(x,y) = 
		\begin{cases}
			\dfrac{\Sigma_i^k\Sigma_j^k W(i,j) \cdot I(x-i,y-j) \cdot M(x-i,y-j)}{\Sigma_i^k\Sigma_j^k W(i,j) \cdot M(x-i,y-j)}, & \text{if}\ \sum_{i}^k\sum_{j}^k M(i,j)>0 \\
			0, & \text{otherwise}
		\end{cases}
	\end{array}
\end{equation}

where $ k $ is the kernel size, $ (x,y) $ is the position in input, $ (i,j) $ is the displacement in kenel, $ M $ is the corresponding mask. A binary mask uses 1 to indicate valid pixels and 0 otherwise. $ \odot $ denotes element-wise multiplication.

Normalized convolution layer added the weight to the mask. However, a initialization for the mask is still required, and the propagation of the mask remain a tricky task.

\subsection{Gated Convolution}

% introduce gconv
\cite{gated_activation} proposed a gated activation unit to model more complex interactions comparing to standard CNN layers, which mainly inspired by the multiplicative units exist in Long Short-Term Memory proposed by \cite{lstm} and Rated Recurrent Unit (GRU) proposed by \cite{gru}. 
\cite{gconv} employed the same gated unit solving for the free-form image inpainting task. The proposed network use 3 channel RGB images as input and estimate the missing pixels.

The structure is shown in Figure \ref{fig:gconvLayer}. Instead of using a mask as input to indicate valid pixels, it employs a standard convolution layers to learn this mask directly from data. The valid pixels are then activated by a Sigmoid function. Then it imply element-wise multiplication with the feature map. Formally, the gated convolution is described as follows, the layer with input size $ (N, C_{in}, H, W) $ and output size $ (N, C_{out}, H_{out}, W_{out}) $:
\begin{equation}\label{gconv}
	o(N_i, C_{o_j}) = \sigma(\sum_{k=0}^{C_{in}-1}w_g(C_{o_j}, k) \star i(N_i,k) + b_g(C_{o_j})) * 
	\phi (\sum_{k=0}^{C_{in}-1}w_f(C_{o_j}, k) \star i(N_i,k) + b_f(C_{o_j}))
\end{equation}
where $ \phi $ is LeakyReLU function, $ \sigma $ is sigmoid function, thus the output values are in range $ [0,1] $, $ \star $ is the valid 2D cross-correlation operator, $ N $ is batch size, $ C $ denotes a number of channels, $ H $ is a height of input planes in pixels, and $ W $ is width in pixels, $ w(C_{o_j},k) $ denotes the weight of $ j $-th output channel corresponding $ k $-th input channel, $ i(N_i, k) $denotes the input of $ i $-th batch corresponding $ k $-th input channel, $ b(C_{o_j}) $ denotes the bias of $ j $-th output channel.

% Gated Convolution Layer
\begin{figure}[th]
	\centering
	\begin{tikzpicture}
		\tikzstyle{rect} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!20]
		\tikzstyle{arrow} = [thick,->,>=stealth]
		\node (output) [rect] {Output};
		\node (oplus) [below of=output, yshift=-.2cm] {$\Huge\oplus $};
		\node (LeakyReLU) [rect,below of=oplus, yshift=-0.4cm] {Feature};
		\node (sigmoid) [rect, below of=oplus, yshift=-0.4cm, xshift=-4cm] {Mask};

		\node (conv1) [rect,below of=sigmoid, yshift=-1cm] {Mask};
		\node (conv2) [rect,below of=LeakyReLU, yshift=-1cm] {Feature};
		\node (input) [below of=oplus] at (0,-7) {\includegraphics[width=.25\textwidth]{./Figures/train-input.png}};

>>>>

The approaches are trained on dataset "synthetic-50-5" as mentioned in Chapter \ref{ch:04} with 3000 scenes. The input matrix has $ 128\times 128 $ height and width. Each vertex map has dimension $ 128\times 128\times3 $, light map has $ 128\times 128 \times 3 $, image has dimension $ 128\times 128 \times 1 $. The model is trained with PyTorch 1.10.0a0, CUDA 11.4.1, GPU with single NVIDIA GEFORCE RTX 3090.

\section{GCNN model evaluation}
The GCNN model is the base model of the whole thesis. In this section, we first discuss the noise filter performance of the model and then evaluate the performance on normal inference.

\subsection{Noise Filter Result}

\begin{figure}[th]
	\centering
	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
	\begin{tikzpicture}
		%% -------------------------------------- parameters ------------------------------------------------
		\pgfmathsetmacro{\vdist}{0.4}

		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3

		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}

		%% 	d_in							3x512x512
		%%	dconv1: 	d_in-->x1 			32x512x512
		\pgfmathsetmacro{\disttimes}{1}	%% width 32
		\pgfmathsetmacro{\yshift}{1}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
		\pgfmathsetmacro{\yschift}{-1}

		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light_input.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};

		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
		{\includegraphics[width=.2\textwidth]{./Figures/intrinsic_image_light.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {Semi-dense Light Map};

		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);

		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
		\pgfmathsetmacro{\yschift}{-1}
		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		\node[text width=3.5cm] at (\vdist*\disttimes,\yschift-1) {Light Net};
	\end{tikzpicture}
	\caption{Light Net for light inpainting based on GCNN architecture.}
	\label{fig:light-net-archi}
\end{figure}

%% nnnn exp
\section{Surface Normal Inference based on Depth Map}
The goal of surface normal inference is to calculate the tangent surface normal map $ N $ from a single depth map $ D $. A network named Gated Convolution Neural Network (GCNN) ( \ref{gcnn}) is trained and is compared with similar approaches. We evaluate the performance of the model in dataset ``synthetic50-5" introduced in  \ref{ch:04} including 5K depth maps with size  $ 512\times512\times3 $ for training. All the depth maps add simulated noise as introduced in \ref{sec:noise}. The training pipeline use batch size $ 8 $,  Adam optimizer (\cite{adam}), learning rate of  $ 1\times10^{-3} $, penalty-l2 loss. The output is directly the tangent normal in range $ \left[-1,1\right] $. The output and input has the same shape.

\subsection{Qualitative Evaluation}

The evaluation visualization on test dataset is shown in Figure \ref{fig:gcnn-eval-synthetic}. As shown in the picture, GCNN model 
Figure \ref{fig:gcnn-eval-synthetic-zoom-in} zooms in the hindhead area of the dragon object which provides a closer comparison with the ground-truth.
\begin{figure}[th]
	\centering
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_point_cloud_noise.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_groundtruth.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_GCNN3-32-512.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_normal_SVD.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_GCNN3-32-512.png}
	\includegraphics[width=0.15\linewidth]{./Figures/comparison/fancy_eval_6_error_SVD.png}
	\caption{GCNN Normal Inference on Synthetic Dataset (object: dragon) From left to right: Input vertex map, ground-truth, GCNN normal map, SVD normal map, GCNN error map, SVD error map}
	\label{fig:gcnn-eval-synthetic}
\end{figure}

\begin{figure}[th]
	\centering
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_input.png}
		\caption{Input}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GT.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_normal_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_GCNN.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}[b]{0.15\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison/eval_2_error_SVD.png}
		\caption{}
	\end{subfigure}
	\caption{Zoom in of dragon object evaluation.}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}

The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
\begin{figure}[th]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_point_cloud_noise.png}
		\caption{point cloud}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_groundtruth.png}
		\caption{ground-truth}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{Evaluation on Real Dataset}
	\label{fig:gcnn-eval-real}
\end{figure}

\subsection{Quantitative Evaluation }

The evaluation result on test scenes is shown in Figure \ref{fig:scatter-gcnn}.
The GCNN based method has angle error between 5 to 15 degrees in both type of inputs. The error trends to higher with point number decrease. It is because the less points in the point cloud, the more detail is hided due to the insufficient of resolution. Therefore the recorded surface based on the point cloud is more coarse, which also increase the difficulty of the normal inference.

\begin{figure}[h!]
	\centering
	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-no-noise.png}
	\includegraphics[width=.4\textwidth]{./Figures/scatter-gcnn-noised.png}
	\caption{Evaluation of average angular loss on the whole test dataset with 90 scenes. The x-axis indicates the point number, the y-axis indicates the angles. The \textbf{Left} one using point cloud without noise, the \textbf{right} one has noise.}
	\label{fig:scatter-gcnn}
\end{figure}

\subsection{Speed}

\section{Guided Gated Convolution Neural Network for Normal Inference }

\subsection{Light Net Evaluation}

We evaluate the GCNN architecture based light net on the test dataset. The light net parameters are further used as the initial parameter of light branch of the Trignet.

A qualitative evaluation of light net is shown in Figure \ref{fig:eval-light}. The average angular error are lower than $ 0.3 $ degree on all of test cases. In this case, to distinguish the output and the ground truth is already not easily only use naked eyes.

\begin{figure}[th]
	\centering
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}

	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}

	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}

	\caption{Qualitative evaluation of light net on Sphere, bus and Washington statue. From left to right, grayscale image, semi-dense light map(input), full-dense light map(output), full-dense light map(ground-truth), error map.}
	\label{fig:eval-light}
\end{figure}

Figure \ref{fig:scatter-light} uses a scatter plot to show the average angular error on 100 different test cases. The average pixel-wise angular error is 0.17 degree as shown in Table \ref{tab:model-error}. An regression line has been added in the plot to analysis the tendency of the errors. The angular error slightly goes up when valid point number in the scene increase. It is make sense since the valid pixels are usually connected and concentrate in a single patch, the less of the area of the patch, which corresponding the number of the valid points, the less variation of the light direction among the pixels, thus better the evaluation.

\begin{figure}[th]
	\centering
	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
	\caption{The evaluation on 100 test cases of Light Net.}
	\label{fig:scatter-light}
\end{figure}

\subsection{Vertex-Image-Light Net (VIL Net) Evaluation}

The qualitative evaluation of VIL net uses the model trained based on masked L2 loss.

\subsubsection{title}

\begin{figure}[th]
	\centering
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_img.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_input.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_light.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_light_gt.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_0_output_error.png}

	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_img.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_input.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_light.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_light_gt.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_1_output_error.png}

	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_img.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_input.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_light.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_light_gt.png}
	\includegraphics[width=0.18\linewidth]{./Figures/light-synthetic/fancy_eval_4_output_error.png}

	\caption{Qualitative evaluation of Trignet net on Sphere, bus and Washington statue. From left to right, semi 3D vertex map, full-dense normal map(output), full-dense normal map(ground-truth), error map.}
	\label{fig:eval-trignet}
\end{figure}

\begin{figure}[th]
	\centering
	\includegraphics[width=0.5\linewidth]{./Figures/scatter-light-noised.png}
	\caption{The evaluation on 100 test cases of Trignet.}
	\label{fig:scatter-trignet}
\end{figure}

\subsection{comparison}
From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension. It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections. Then it counts the number of points locates in each section for 3 axes.  The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis. Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.

It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
\begin{figure}[th]
	\centering
	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff.png}
	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively. The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis. (The chart is based on the "dragon" scene showing above)}
	\label{fig:normal-histo-diff}
\end{figure}

\begin{table}[th]

	\centering
	\begin{tabular}{l l l l l l l l }
		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.} & over-perform\\
		LightNet  & 0.17  & 4.72 & &  & & & \\ 
		\hline
		GCNN  & 10.57 & 5.25 & 8 & 200,1600 & 0.5 & 0 & - \\
		\hline
		an3 & 10.46 & 64.86 & 8 & 3,12,1000  & 0.5 & 1 & yes\\
		\hline
		an3 & 10.81 & 65.34 & 8 & 10,1000  & 0.5 & 1 & no(yes) \\
		\hline
		VIL-1 & 10.50 & 31.57 & 8 & 10,1000 & 0.5 & 1 & yes \\
		\hline
		VIL-1 & 10.82 & 32.61 & 8 & 3,12,1000 & 0.5 & 1 & no(yes) \\
		\hline
		VIL-3  & 10.79 & 54.76 & 8 & 100,1000 & 0.1 & 3 & no(yes) \\
		\hline
		VIL-10  & 11.10 & 132.32 & 8 & 100,1000 & 0.1 &10 & no(yes)\\
	\end{tabular}
	\caption{The error of models. The angle error is the average angle error of all valid pixels in the test case. The time unit is millisecond. bz is the batch size, lr-schedule is learning rate schedule. lr-df is learning rate decay factor, l/i. Nr is the number of light-image maps used for each scene}	
	\label{tab:model-error}
\end{table}

\begin{figure}[th]
	\centering
	\includegraphics[width=\linewidth]{./Figures/regression-comparison.png}
	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively. The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis. (The chart is based on the "dragon" scene showing above)}
	\label{fig:normal-histo-diff}
\end{figure}
